\vspace{-2.0em} Move Schedules: \\ Fast persistence computations in sparse dynamic settings\thanks{This work was partially supported by the National Science Foundation through grants CCF-2006661 and CAREER award DMS-1943758.}\vspace{-0.5em}

### 2021-08-04 move_schedules.tex
Wrapping up changes to the last paragraphs

A priori, had one not been aware of the analysis done by~\cite{lee2003nonlinear, hateren_schaaf_1998, carlsson2008local, perea2014klein}, there is no specific reason to assume the data are well-approximated by the Klein bottle specifically.

>>>>

If one was not aware of the analysis done by~\cite{lee2003nonlinear, hateren_schaaf_1998, carlsson2008local, perea2014klein}, there is no specific reason apriori to assume the data are well-approximated by the Klein bottle. Consider the (coarsened) fibered barcode shown in Figure~\ref{fig:patch_data_dgm} which was computed from a standard Rips/codensity bifiltration on a constructed on a representative sample of the image data from~\cite{hateren_schaaf_1998} (how we obtained this sample is described further down). Upon inspection of the bigraded Betti number and the dimension function, one finds that a large area of dimension function is constant (highlighted as the blue portion in the middle of Figure~\ref{fig:patch_data_dgm}), wherein $\mathrm{dim}(M) = 5$. This indicates
